---
title: "Homework 1"
author: Çağla Çetiner 19080388
---

```{r global_options, include=FALSE}
# Do not delete or modify this chunk.
# We will cover chunk options later.
# This is required for Question 7
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**Question 1** With Markdown write a sentence that has one word in bold.

The oldest known pet **cat** existed 9500 years ago.

**Question 2** With Markdown write a sentence that has one word in italic.

Cats spend 70% of their lives *sleeping*.

**Question 3** With Markdown write a sentence that has one word in italic bold.

A cat was the Mayor of an ***Alaskan*** town for 20 years.

**Question 4** With Markdown write an unordered list with three items.

##### A few of your cat's favorite things

\* Cats love sleeping and napping.<br> \* Cats need to scratch.<br> \* Cats love high places for watching and hiding.<br>

**Question 5** With Markdown write an ordered list with three items.

##### How Cats Choose Their Favorite Human

1.spend more time with them.<br> 2.match thie interests.<br> 3.talk to them.<br>

**Question 6** With Markdown give a link to your favorite webpage.

If you are wondering more, you can check [this page.](https://www.purina.co.uk/articles/cats/behaviour/common-questions/fun-facts-about-cats)

**Question 7** With Markdown add a cat picture.

![](images/kedii%20(1)-02.jpeg){width="307"}

[one of our street cats]{style="color: red;"}

**Question 8** With Rmarkdown insert a code chunk and give an example of a simple mathematical calculation in it.

```{r}
x <- 82
sqrt(9) + x/2 + 4^4
```

**Question 9** With $LaTeX$ write your favorite equation in block form.$$
f(n) = n^6 + 2n^5 + 6 |_{n=5}
$$

**Question 10** In a code chunk calculate 3 + 4.

```{r}
3+4
```
